---
title: "testemail"
author: "Office of Marketing and Brand Management"
date: "6/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(gt)
library(blastula)
library(tidyverse)
library(ggplot2)
library(glue)
library(formattable)

```

```{r}


# Create the plot data
variety <- rep(LETTERS[1:7], each = 40)
treatment <- rep(c("high", "low"), each = 20)
note <- seq(1:280) + sample(1:150, 280, replace = TRUE)
data <- data.frame(variety, treatment, note)

# Create the plot
the_plot <-
  ggplot(data, aes(x = variety, y = note, fill = treatment)) + 
  geom_boxplot()+theme_bw()



# Send your ggplot to Imgur with a Client Key;
# again, you get an <img> tag that works for email
imgur_image <-
   add_imgur_image(
     image = the_plot,
     client_id = "851117406f0b457"
   )

#
# Create the `body_text` and then the
# email message with `compose_email()`
#
body_text <-
  glue(
    "
Hello,

I just wanted to let you know that the *ggplot* you \\
wanted to see is right here, in this email:

{imgur_image}

Cheers,

christineiyer
"
  ) %>% md()

compose_email(body = body_text) %>%
  smtp_send(
    to = "edithbird5@gmail.com",
    from = "christine.iyer@maine.edu",
    subject = "Testing the `Send Plot",
    credentials = creds_key(id = "gmail")
  )
```

Save Table as Image to Imgur then send as Email


```{r}

#save table as image
Sample <- read.csv("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/Sample.csv", header = T, stringsAsFactors = F)
png("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/output.png", width=480,height=480,bg = "white")
grid.table(Sample)
dev.off()
# kable(Sample)
```

Hi John,

I'm wondering if you have a little free time today for a zoom. 

As I think I mentioned, now that the FileMaker is established, my role now is to incorporate the Weekly Admission Report into a simple quarterly summary that provides them with insights that will drive optimization of resources.

In order to build this report, I want to make sure I understand it completely. One thing that confuses me is the admission period. The FM reports shift to the next academic year on September 1 while our fiscal summary runs through September 30. I'm trying to figure out if there is a way to see this same data quarterly

Another question that I want clarification on  is making sure I'm pulling from the correct data fields in the reports. 

The summary will ultimately look like the table attached 


Thank you, 



Christine Iyer

Data Analyst  



Office of Marketing and Brand Management 

47 Exeter St. 

Portland, ME 04102 

Office: 207-780-4692

```{r}
imgur_image <-
   add_imgur_image(
     image = "C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/output.png",
     client_id = "851117406f0b457"
   )

#
# Create the `body_text` and then the
# email message with `compose_email()`
#
body_text <-
  glue(
    "
    
    Hi John,

I'm wondering if you have a little free time today for a zoom. 

As I think I mentioned, now that the FileMaker is established, \\
I will now incorporate the Weekly Admission Reports into a \\
simple quarterly summary that provides them with insights that will \\
drive optimization of resources. \\

In order to build this report, I want to make sure I understand it \\
completely. One thing that confuses me is the admission period. Your reports \\
shift to the next academic year on September 1 while our fiscal summary runs \\
through September 30. I'm trying to figure out if there is a way to see this same data quarterly.\\

Another question that I want clarification on is making sure I'm pulling \\
from the correct data fields in the reports. \\

The summary will ultimately look like this table \\

{imgur_image}

Cheers,

Christine Iyer
"
  ) %>% md()

compose_email(body = body_text) %>%
  smtp_send(
    to = "john.tabor@maine.edu",
    from = "christine.iyer@maine.edu",
    subject = "Weekly Admissions Reports",
    credentials = creds_key(id = "gmail")
  )
```

## Alternatively, can just send an image by skoipping the 

```{r}
# CappexNames <- read.csv("C:/Users/christine.iyer/Box/Cappex Leads FY20/FY20CappexLeads.csv", header = T, stringsAsFactors = F)
# 
# states <- c("ME", "NH", "MA", "CT")
# Table <- CappexNames %>% 
#   mutate(StateRegion = ifelse(State %in% states, "New England", "Outside NE")) %>% 
#   group_by(State) %>% summarise(n = n()) 
```


```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Get a nicely formatted date/time string
# date_time <- add_readable_time()
# 
# # Create an image string using an on-disk
# # image file
# img_file_path <-
#   system.file(
#     "img", "pexels-photo-267151.jpeg",
#     package = "blastula"
#   )
# 
# img_string <- add_image(file = img_file_path)
# }
# date_time <- add_readable_time()
# formatted_table <- format_table(Table)
# 
# email <-
#   compose_email(
#     body = md(
#       c(
# "Hello,
# 
# This is a *great* table I found when looking
# for looking through the data:
# ",
# formatted_table
#       )
#     ),
# footer = md(
#   c(
#     "Email sent on ", date_time, "."
#   )
# )
#   )
```

Imgur Data 
Great! Now you can get started with the API!
For public read-only and anonymous resources, such as getting image info, looking up user comments, etc. all you need to do is send an authorization header with your client_id in your requests. This also works if you'd like to upload images anonymously (without the image being tied to an account), or if you'd like to create an anonymous album. This lets us know which application is accessing the API.

Authorization: Client-ID YOUR_CLIENT_ID

For accessing a user's account, please visit the OAuth2 section of the docs.

Client ID:
851117406f0b457
Client secret:
7bae767f52737d95ed4136bb77b7c91738de21c8




